Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-09-26 response.tex

\comment{58}{%
P37: 10 percent of probability $\to$ 10 percent probability }
\response{Response will be here.}

\comment{59}{%
p 39,figure 11: Include horizontal lines indicating 2 and 10\% probability of exceedance in 50 years.}
\response{Included.}

\comment{60}{%
p 41, figure 12: Can you include curves or points for the other studies in Table 3?}
\response{Response will be here.}

\introcomment{~}{%
Summary of modifications (Remove before submitting)\\
- Buffer zone updated.\\
- Data updated.\\
- b-values updated.\\
- Completeness parameters updated.\\
- Figure 1: Buffer Zone Updated.\\
- Figure 3: Seismicity.sh modified. Historical.txt and Instrumental.txt updated to new data. \\
- Figure 4: Updated.\\
- Figure 5: The excel file is updated. The figure needs to be updated.\\
- Figure 6: Updated data completeness plots added to the figure. Figure needs final polishing. \\

}

### 2016-09-27 response.tex

\comment{4}{%
Pp 6, line 168: It would be good to add a reference for the GEM effort.
}

\response{%
Response will be here.
}

\comment{5}{%
Pp7-8: Discussion about identifying the completeness level of the earthquake catalogs is a bit confusing. Typically, one either specifies a minimum magnitude of completeness (Mc) and then tries to identify the earliest time for which events or complete; or, one specifies a year and computes the corresponding Mc. In reading the text, it appears that both methods were used. Please clarify.
}

\response{%
You are right. We used both methods in the study. First we compute the $b-value$ and $M_{max}$ for each region, or the uniform model using the HA3 package written by Dr. Kijko. $M_c$ is used as an input in the software to get accurate results. We computed the smoothed seismic hazard using the Seiskit package, written by Dr. Frankel. In estimating the seismic hazard, specifically $a-value$, we need to define a start year of completeness for each magnitude range. We modified the text to clarify the statement. 
}

@@

\introcomment{~}{%
Review of Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity by Naeem Khoshnevis, Ricardo Taborda, Shima Azizzadeh-Roodpish, and Chris H. Cramer
}

\introcomment{~}{%
In this paper, the researchers present a new seismic hazard analysis of northern Iran. The paper makes use of the latest available data and methods, is thorough in its review of previous work, and is very well presented and written. I have a few suggestions that I think would improve the impact of their results. The annotated version of the manuscript contains additional and more specific suggestions.
}

\comment{1}{%
The authors present uncertainty in their hazard estimate but do not include a more exhaustive logic tree analysis. Effectively, they have two branches: a regional model and uniform model. It appears that they apply the aleatory uncertainty in the ground motion prediction relation to a form of epistemic uncertainty, effectively double counting this uncertainty in the hazard analysis. I would prefer to see a more standard logic tree analysis where multiple GMPEs (or a backbone plus and minus one standard deviation) and uncertainty in a-value, b-value, and Mmax, for example, are considered. Barring this analysis, I would remove figure 10 and references to hazard uncertainty.
}

\response{Thanks for the comment.  Based on explanation of GMPEs section (please see comment no.?) we decided to define a suite of GMPE and also provide the uncertainty. We consider the epistemic uncertainty, based on defining two different model (which considers the uncertainty in $b-value$ and $M_max$). In order to make it clear we added two GMPE suites (plus and minus one standard deviation) also we defined the uncertainty in $M_{max}$. This approach will cover the most of uncertainty in the study.}.

@@

\response{That right. We increased the buffer zone up to 2 degrees. (Haven't modified the text)}

\comment{3}{%
It would be good if the abstract is more specific about the results. Where is the hazard greatest? What sources contribute to regions of higher hazard?
}
\response{Response will be here.}

\comment{4}{%
In the second paragraph of the introduction, I would include a reference to a figure of the region to help readers less familiar with the area. This figure should also be referred to in subsequent paragraphs. It is probably sufficient to move reference to figure 1 here.
}
\response{Response will be here.}

\comment{5}{%
line 39:   eight  $\to$ eighth
}
\response{Fixed.}

\comment{6}{%
line 55   focuses in $\to$ focuses on
}
\response{Done. Thanks.}

\comment{7}{%
line 56 $\to$ Please be more specific about how your analysis differs from previous analyses.
}
\response{Response will be here.}

\comment{8}{%
line 60 $\to$ Can you be more specific? What are the other indicators?
}
\response{Response will be here.}

\comment{9}{%
line 71 $\to$ Include reference? Include reference.
}
\response{Done. Thanks.}

\comment{10}{%
line 78 $\to$ reduce $\to$ acknowledge
}
\response{Fixed.}

\comment{11}{%
line 99 $\to$ Is 0.5 degrees enough? To what distance do you do your ground motion calculations? In the western United States, they are done to 200 km. In the central and eastern, they are done to 1000 km. Depending on this value, you should include sources up to this distance from your region of interest.
}
\response{We reanalyze the hazard with 2 degrees buffer zone. (Not modified in the text.)}

\comment{12}{%
line106 $\to$ northeast $\to$ northwest
}
\response{Done. Thanks}

\comment{13}{%
line 114 $\to$ There is no previous mention of this earthquake. I am not sure to which earthquake you are referring. Should either the 1721 or 1780 earthquakes be the Shebli earthquake?
}
\response{Thanks for the comment. It is 26 April 1721,$M_s ~ 7.3$ earthquake}

\comment{14}{%
line 180 $\to$ The smaller events should also help to inform the G-R relationship.
}
\response{Thanks for the comment. Added to the text.}

\comment{15}{%
line 182 $\to$ How come this study doesn't appear in Table 3. Do they not calculate PGA for 2 and 10\% exceedance in 50 years?
}
\response{Response will be here.}

\comment{16}{%
line 192 $\to$ What is the total number of events before and after declustering?
}
\response{Number of events before decluttering: 10441, total foreshock: 971, total aftershock: 4206, declustered data 5254. It should be noted that, these numbers are representing the events in the study region (including the bufferzone). It partly includes events from Central and Zagros region. For completeness study we studied the whole data for each region.}

\comment{17}{%
line 224 $\to$ Why did you use this method? What are the benefits of one or the other?
}
\response{Response will be here.}

\comment{18}{%
line 232 $\to$ It is unclear how you chose Mc. In some cases, it looks like you chose the peak goodness-of-fit value, but in others you did not. Please be more specific about how Mc was chosen.
}
\response{Response will be here.}

\comment{19}{%
line 267 $\to$ add 'and'
}
\response{Added. Thanks.}

\comment{20}{%
line 289 $\to$ You might also cite the 2014 USGS National Model (Petersen et al., 2014) and the Afghanistan seismic hazard maps (Boyd et al, 2007), which include spatial variability in the smoothing parameter.
}
\response{Added. Thanks.}

\comment{21}{%
line 297 $\to$ provided below $\to$ provided in the next section
}
\response{Fixed.}

\comment{22}{%
line 300 :  allows to draw information $\to$ allows one to draw information 
}
\response{Done.}

\comment{23}{%
line 323 $\to$ Be more specific about how HA3 computes b and Mmax. What is its method?
}
\response{Method added. Thanks.}

\comment{24}{%
line 335 $\to$ Different seismic zone will not necessarily have difference values of b and Mmax. Change to this: Different seismic zone may have different values of b and Mmax.
}
\response{Response will be here.}

\comment{25}{%
line 337 $\to$ a means to reduce epistemic $\to$ a means to account for epistemic 
}
\response{Done.}

\comment{26}{%
line 361 $\to$ lead $\to$ leads
}
\response{Two reviewer suggested two different word. Both of them are correct. Please see.}

\comment{27}{%
line 364 $\to$ How do you address the epistemic uncertainty generally introduced by using a suite of GMPEs?
}
\response{As mentioned in Atkinson and Adam (2013) and Atkinson et al (2014), using different GMPEs with different logic tree weights from different literature is not necessarily the best way to model the epistemic uncertainty in GMPEs. We prefer to use the alternative GMPEs and applicable data to guide the choice of a representative or ?central? GMPE, and to define representative (upper and lower) GMPEs that express uncertainty about the central GMPE. In the previeous study (Khodaverdian 2016), they used Akkar and Bommer (2010) and Ghasemi et al (2009) along side other equations. Akkar and Bommer (2010) derived the equation up to 100 Km, which they used for 200 km. Also Ghasemi et al (2009) is presented the coefficients for spectral acceleration not PGA. Of course this alternative method has been a hotly-debated topic, and there is no clear consensus about that, however, the plots of attenuation relationships in different magnitude illustrate the fact that with this approach we can address the epistemic uncertainty in an acceptable range. We totally agree with the reviewer?s comment that presenting the seismic hazard with upper and lower values (Fig 10) to address the epistemic uncertainty could be misleading for the readers. In order to address these concerns, we do the seismic hazard analysis for bigger domain (2 degrees buffer zone) and combine the results according to the logic tree scheme in Fig X.}

@@

\comment{28}{%
line 365: add 'and'
}
\response{Added. Thanks.}

\comment{29}{%
line 370 $\to$ Could you consider other depths to help fill out your range of epistemic uncertainty?
}
\response{The Kalkan and Gulkan (2004) attenuation relationship is originally generated for Turkey. However, in the recent test by Zafarani and Mousavi (2014), it gives acceptable results for PGA. Since the high accuracy achieved by the current depth, and we have no idea how different depth will change the results, we prefer to not to use a parameter without knowing the effects. }

\comment{30}{%
line 371 $\to$ How does this value compare with the models you decided not to use?
}
\response{Response will be here.}

\comment{31}{%
line 376 $\to$ In this case, you should consider all sources with 200 km of your area of interest.
}
\response{We modified the buffer zone. Thanks.}

\comment{32}{%
line 394:  50-years $\to$ 50-year
}
\response{Done.}

\comment{33}{%
line 420: with concentration $\to$ with a concentration
}
\response{Added. Thanks.}

\comment{34}{%
line 422 $\to$ I would have stated this differently. It looks like the lower b-value in Kopeh Dagh yields relatively high hazard in the R model whereas in the U model, this low b-value has leaked into the entire region and subsequently elevated seismic hazard in all areas outside of Kopeh Dagh.
}
\response{Response will be here.}

\comment{35}{%
line 428 $\to$ Why equal weights?
}
\response{Response will be here.}

\comment{36}{%
line 431 $\to$ I'm not sure I quite understand this. The standard deviation in the attenuation relation is considered aleatory uncertainty and is present within the hazard curve. Adding it as epistemic as well will cause double counting. If you want to include figure 10, a proper logic tree analysis to include more forms of epistemic uncertainty should be performed. For example, add branches for uncertainty in which GMPE you choose, uncertainty in b-value, uncertainty in Mmax, uncertainty in a-value, uncertainty in smoothing parameter, etc.
}
\response{We modified the approach and considered the mentioned uncertainties.}

\comment{37}{%
line 434 $\to$ Just because the basic pattern appears to better follow faults in the region does not mean it's a better assessment, especially if the b-values are truly different between regions and better represented by the regional analysis.
}
\response{Response will be here.}

\comment{38}{%
line 439: of city of Tabriz $\to$ of the city of Tabriz.
}
\response{Fixed. Thanks.}

\comment{39}{%
line 450 $\to$  for 2 and 10\%, respectively $\to$ for 2 and 10\% in 50 years, respectively.
}
\response{Done.}

\comment{40}{%
line 453 $\to$  for a 10\% probability of exceedance ?  for a 10\% probability of exceedance in 50 years.
}
\response{Done.}

\comment{41}{%
line 455 $\to$ 0.27-0.31 g for 10\% probability of exceedance $\to$  0.27-0.31 g for the same exceedance probability
}
\response{Done.}

\comment{42}{%
line 458 $\to$  for 2 and 10\% ? for 2 and 10\% in 50 years
}
\response{Done.}

\comment{43}{%
line 461: our results are close or within $\to$ our results are close to or within 
}
\response{Done.}

\comment{44}{%
line 462 $\to$ Can you explain the differences in their analysis relative to yours that lead to higher values?
}
\response{Response will be here.}

\comment{45}{%
line 466 $\to$ exceedance as functions of PGA ? exceedance as functions of PGA, also known as hazard curves}
\response{Added. Thanks.}

\comment{46}{%
line 475 $\to$ Can you explain the differences in the hazard analysis that led to differences in hazard?}
\response{Response will be here.}

\comment{47}{%
line 462 $\to$ Can you explain the differences in their analysis relative to yours that lead to higher values?
}
\response{Response will be here.}

\comment{48}{%
lline 488 $\to$ Not sure you can say this because you don't include fault specific sources, and you do not consider a more full range of epistemic uncertainty, e.g. you only use one GMPE (though you do consider two b-value and Mmax based models).
}
\response{Response will be here.}

\comment{49}{%
line 488:  hazard analysis $\to$ hazard analyses
}
\response{Done.}

\comment{50}{%
line 490: models as a mean $\to$ models as a means}
\response{Done.}

\comment{51}{%
line 493 $\to$ Though you suggest the uniform model is unrealistic on line 334.}
\response{Response will be here.}

\comment{52}{%
line 502 $\to$ for providing advise ? for providing advice}
\response{Done.}

\comment{53}{%
line 509 $\to$  Should this be Sunset?}
\response{Yes. Thanks.}

\comment{54}{%
p 25 ? table2 $\to$ What did you do for the earthquakes occurring outside of these five zones?}
\response{There are earthquakes out of the regions, mainly above the Caspian see. Since those area are not in our region of interest, and are fairly far from our region, we ignored them.}

\comment{55}{%
p 26 ? table3 $\to$ Specify units.}
\response{Response will be here.}

\comment{56}{%
p32 ? figure 3 $\to$ You should also show events in the buffer zone used to compute hazard.}
\response{Done.}

\comment{57}{%
p34 ? figure 5 $\to$ Which seismic zone corresponds to which color? It looks like either reporting or rates have changed over time. For example, I might argue that the red region was not complete for M3 and above until 2005. }
\response{Response will be here.}

### 2016-09-27 acknowledge.tex
Couple of comments were addressed.

The authors wish to express their gratitude to Art Frankel at the U.S.~Geological Survey (USGS) for providing access to the Smoothed Probabilistic Seismic Hazard Analysis software and to Morgan Moschetti, also at the USGS, for providing advise on the use of the software. The authors also thank Andrzej Kijko at the University of Pretoria for providing access to the software for computing the seismicity parameters; and Mehdi Zare at the International Institute of Earthquake Engineering and Seismology (IIEES) in Tehran for kindly providing the original catalog data and for his assistance in interpreting previous catalog information. Access to data provided by IIEES is also greatly appreciated. This research was possible thanks to support by the Center for Earthquake Research and Information (CERI) at the University of Memphis. CERI is designated as a Center of Excellence by the Tennessee Board of Regents and is funded in part by the State of Tennessee under State Sunsent Laws (SB 1510 and HB 1608, 2015--2016).

>>>>

The authors wish to express their gratitude to Art Fran\-kel at the U.S.~Geological Survey (USGS) for providing access to the Smoothed Probabilistic Seismic Hazard Analysis software and to Morgan Moschetti, also at the USGS, for providing \myrevision{advice} on the use of the software. The authors also thank Andrzej Kijko at the University of Pretoria for providing access to the software for computing the seismicity parameters; and Mehdi Zare at the International Institute of Earthquake Engineering and Seismology (IIEES) in Tehran for kindly providing the original catalog data and for his assistance in interpreting previous catalog information. Access to data provided by IIEES is also greatly appreciated. This research was possible thanks to support by the Center for Earthquake Research and Information (CERI) at the University of Memphis. CERI is designated as a Center of Excellence by the Tennessee Board of Regents and is funded in part by the State of Tennessee under State \myrevision{Sunset} Laws (SB 1510 and HB 1608, 2015--2016).

### 2016-09-27 completeness.tex
Couple of comments were addressed.

An important aspect of seismic catalogs is their completeness. This characteristic is measured in terms of the start-year of completeness and the completeness magnitude, which are both parameters that are later used in the seismic analysis process. The start-year of completeness is the point in time at which catalog data exhibit a steady rate of event occurrence or record accumulation for a certain magnitude range, and the completeness magnitude ($M_c$) is the magnitude above which the seismic catalog of a region can be considered complete within a certain time period.

>>>>

An important aspect of seismic catalogs is their completeness. This characteristic is measured in terms of the start-year of completeness and the completeness magnitude, which are both parameters that are later used in the seismic analysis process. The start-year of completeness is the point in time at which catalog data exhibit a steady rate of event occurrence or record accumulation for a certain magnitude range \myrevision{which in this study we use these values in estimating $a-values$ of smoothed seismic hazard, and the completeness magnitude ($M_c$) is the magnitude above which the seismic catalog of a region can be considered complete within a certain time period. \myrevision{ We use $M_c$ for each catalog to compute the $b-value$ and $M_{max}$}

### 2016-09-27 conclusions.tex
Couple of comments were addressed.

We present results from a seismic hazard analysis for northern Iran based on a smoothed seismicity approach, including regional maps of expected peak ground accelerations for different seismic zonation models. In particular, we calculated the hazard for the region of interest using two basic models, a five-seismic zone regions model and a uniform seismic zone model. Our calculations yield results similar to those of other studies but offer a more complete picture than previous hazard analysis due to the usage of a more complete catalog and inclusion of low-magnitude events. In our analysis we found it convenient to combine both the regional and uniform models as a mean to consider the epistemic uncertainty intrinsic to the subjective choice of models and seismic zones. Such a combination yielded hazard maps that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, and to the location of known seismically active faults. While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural areas that are not the subject of specialized hazard studies such as those conducted for major urban centers. Future work to improve the results presented here should consider alternative attenuation relationships, especially for estimating other ground motion parameters such as response spectral accelerations for different periods and site effects.

>>>>

We present results from a seismic hazard analysis for northern Iran based on a smoothed seismicity approach, including regional maps of expected peak ground accelerations for different seismic zonation models. In particular, we calculated the hazard for the region of interest using two basic models, a five-seismic zone regions model and a uniform seismic zone model. Our calculations yield results similar to those of other studies but offer a more complete picture than previous hazard \myrevision{analyses} due to the usage of a more complete catalog and inclusion of low-magnitude events. In our analysis we found it convenient to combine both the regional and uniform models as a \myrevision{means} to consider the epistemic uncertainty intrinsic to the subjective choice of models and seismic zones. Such a combination yielded hazard maps that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, and to the location of known seismically active faults. While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural areas that are not the subject of specialized hazard studies such as those conducted for major urban centers. Future work to improve the results presented here should consider alternative attenuation relationships, especially for estimating other ground motion parameters such as response spectral accelerations for different periods and site effects.

### 2016-09-27 hazard.tex
Couple of comments were addressed.

In this study we use the smoothed seismicity method introduced by \citet{Frankel1995}. This method has been used successfully in different regions around the world including Alaska, California, Hawaii, Italy, \myrevision{and} Turkey \citep[e.g.,][]{Cao1996, Klein2001, Akinci2004, Kalkan2009, Moschetti2014}. In it, the $b$-value is commonly assumed constant within a given seismic zone of ``homogeneous'' seismogenic characteristics, whereas $a$ is varied spatially according to the cataloged occurrence of earthquakes within and around the region. The spatial variation of $a$ is defined based on dividing the region of interest into regular-size grid cells. The parameter $a$ is determined based on the number of events $n_i$ within each cell $i$ of magnitude greater than a reference value $M_{\mathrm{ref}}$, and discretized in different magnitude ranges (or bins). The number of earthquakes within each cell is then smoothed spatially taking into account the values of neighboring cells using a Gaussian function. In essence, the smoothed seismicity approach addresses the aleatoric uncertainty of future earthquake locations by using a weighted contribution of the background regional seismicity, and thus eliminates the need for knowledge about specific fault locations.

In this study we discretize the region of interest into a regular grid with cells of size 0.1\textdegree{} $\times$ 0.1\textdegree{} (in longitude and latitude). The parameter $a$ for each cell is obtained based on the information in the seismic catalog described in the previous section. Following \citet{Frankel1995}, $n_i$ is smoothed using the normalized Gaussian function
% 
\begin{equation}
	\tilde{n}_i = \frac
		{ \sum_{j} n_{j} \exp ( \frac{ -\Delta_{ij}^{2} }{ c^2 } ) }
		{ \sum_{j} \exp ( \frac{ -\Delta_{ij}^{2} }{ c^2 } ) }
	\, ,
	\label{eq:nnorm}
\end{equation}
% 
where $\tilde{n}_i$ is the smoothed, normalized number of events in cell $i$, $\Delta_{ij}$ is the distance between the $i$-th and $j$-th cells, and $c$ is the correlation distance. The summations in Eq.~\ref{eq:nnorm} are calculated over the number of $j$ cells within a distance $3c$ from the $i$-th cell. It should be noted that in this process we convert the cumulative number of events to incremental values following \citet{Herrmann1977}. We also note that according to \citet{Frankel1995}, moderate earthquakes generally occur in areas where there have been significant numbers of events with magnitudes $M \geq 3$, thus our interest in having augmented the earthquake catalog for events above this threshold.

It is obvious from Eq.~\ref{eq:nnorm} that an important parameter in smoothing the seismicity is the correlation distance. Different values of $c$ have been used in past studies, ranging between 10 and 50 km. \citet{Frankel1995} and \citet{Boyd2008} assumed a correlation distance of 50~km, \citet{Foteva2006} used 10 and 15 km, \citet{Barani2007} used 25~km, and \citet{Khodaverdian_2016_BSSA} used 40 km. According to \citet{Mirzaei1997}, determining an appropriate value of $c$ depends on the crustal structure of the region, the distribution of stations, and the number and quality of records. We use an intermediate value of $c=30$~km. This selection is consistent with epicentral uncertainty for previous hazard zoning maps for Iran \citep[see][]{Zare2012}.

>>>>

In this study we use the smoothed seismicity method introduced by \citet{Frankel1995}. This method has been used successfully in different regions around the world including Alaska, California, Hawaii, Italy, \myrevision{and} Turkey \myrevision{\citep[e.g.,][]{Cao1996, Klein2001, Akinci2004, Kalkan2009, Moschetti2014,Kagan1994}}. In it, the $b$-value is commonly assumed constant within a given seismic zone of ``homogeneous'' seismogenic characteristics, whereas $a$ is varied spatially according to the cataloged occurrence of earthquakes within and around the region. The spatial variation of $a$ is defined based on dividing the region of interest into regular-size grid cells. The parameter $a$ is determined based on the number of events $n_i$ within each cell $i$ of magnitude greater than a reference value $M_{\mathrm{ref}}$, and discretized in different magnitude ranges (or bins). The number of earthquakes within each cell is then smoothed spatially taking into account the values of neighboring cells using a Gaussian function. In essence, the smoothed seismicity approach addresses the aleatoric uncertainty of future earthquake locations by using a weighted contribution of the background regional seismicity, and thus eliminates the need for knowledge about specific fault locations.

In this study we discretize the region of interest into a regular grid with cells of size 0.1\textdegree{} $\times$ 0.1\textdegree{} (in longitude and latitude). The parameter $a$ for each cell is obtained based on the information in the seismic catalog described in the previous section. Following \citet{Frankel1995}, $n_i$ is smoothed using the normalized Gaussian function
% 
\begin{equation}
	\tilde{n}_i = \frac
		{ \sum_{j} n_{j} \exp ( \frac{ -\Delta_{ij}^{2} }{ c^2 } ) }
		{ \sum_{j} \exp ( \frac{ -\Delta_{ij}^{2} }{ c^2 } ) }
	\, ,
	\label{eq:nnorm}
\end{equation}
% 
where $\tilde{n}_i$ is the smoothed, normalized number of events in cell $i$, $\Delta_{ij}$ is the distance between the $i$-th and $j$-th cells, and $c$ is the correlation distance. \myrevision{An alternative smoothing kernel has been used in recent studies \citep[e.g.][]{Moscheti2015}}.The summations in Eq.~\ref{eq:nnorm} are calculated over the number of $j$ cells within a distance $3c$ from the $i$-th cell. It should be noted that in this process we convert the cumulative number of events to incremental values following \citet{Herrmann1977}. We also note that according to \citet{Frankel1995}, moderate earthquakes generally occur in areas where there have been significant numbers of events with magnitudes $M \geq 3$, thus our interest in having augmented the earthquake catalog for events above this threshold.

It is obvious from Eq.~\ref{eq:nnorm} that an important parameter in smoothing the seismicity is the correlation distance. Different values of $c$ have been used in past studies, ranging between 10 and 50 km. \citet{Frankel1995},\myrevision{\citet{Boyd2007},  \citet{Boyd2008}, and \citet{Petersen2015}}  assumed a correlation distance of 50~km, \citet{Foteva2006} used 10 and 15 km, \citet{Barani2007} used 25~km, and \citet{Khodaverdian_2016_BSSA} used 40 km. According to \citet{Mirzaei1997}, determining an appropriate value of $c$ depends on the crustal structure of the region, the distribution of stations, and the number and quality of records. \myrevision{Also some studies employ likelihood testing of smoothed seismicity rate models to identify optimal smoothing length for adaptive and fixed smoothed seismicity methods \citep[e.g.][]{Werner2011,Moscheti2015}}. We use an intermediate value of $c=30$~km. This selection is consistent with epicentral uncertainty for previous hazard zoning maps for Iran \citep[see][]{Zare2012}.

### 2016-09-27 introduction.tex
Couple of comments were addressed.

Most previous studies focus on particular locations or are based on specific categorization of seismogenic faults, which are often subjectively interpreted and limited to data availability. We use the smoothed seismicity method introduced by \citet{Frankel1995}. This approach has been used with success in other regions \citep[e.g.][]{Cao1996, Akinci2004, Kalkan2009}, including Iran \citep{Khodaverdian_2016_BSSA}. Its major feature is the treatment of cataloged instrumental and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting. While we recognize that probabilistic seismic hazard analysis based on fault systems can be more realistic and accurate, by choosing the smoothed seismicity method we seek to \myrevision{acknowledge} the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored. In our analysis, we assume earthquake hazard in northern Iran to be dominated by the seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh, but also consider the contribution of the areas of Zagros and the central-east seismic zones to the hazard calculation within our domain of interest (see Fig.~\ref{fig:iran}). In addition to this five seismic-zone model, we obtain results for the entire region of interest as if it could be considered as a single uniform seismic zone. We used both these models and the combination of them to interpret seismic hazard in northern Iran.

>>>>

\myrevision{Most previous studies focus on particular locations  based on specific categorization of seismogenic faults citep[e.g.][]{Ghodrati2003,Vafai2011,Abdi2013}, which are often subjectively interpreted and limited to data availability.} We use the smoothed seismicity method introduced by \citet{Frankel1995}. This approach has been used with success in other regions \citep[e.g.][]{Cao1996, Akinci2004, Kalkan2009}, including Iran \citep{Khodaverdian_2016_BSSA}. Its major feature is the treatment of cataloged instrumental and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting. While we recognize that probabilistic seismic hazard analysis based on fault systems can be more realistic and accurate, by choosing the smoothed seismicity method we seek to \myrevision{acknowledge} the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored. In our analysis, we assume earthquake hazard in northern Iran to be dominated by the seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh, but also consider the contribution of the areas of Zagros and the central-east seismic zones to the hazard calculation within our domain of interest (see Fig.~\ref{fig:iran}). In addition to this five seismic-zone model, we obtain results for the entire region of interest as if it could be considered as a single uniform seismic zone. We used both these models and the combination of them to interpret seismic hazard in northern Iran.

### 2016-09-27 parameters.tex
Couple of comments were addressed.

The $a$-value is estimated based on the completeness year, the correlation distance, and the number of events per grid cell. We assume magnitude increments of $\Delta M = 0.1$, count events with magnitude $M_w > 3$, and smooth the number of events for each cell. This means each cell has a different $a$-value and thus the result is variable throughout our region of interest. On the other hand, we consider the $b$-value and $M_{\max}$ to be constant within each of the seismic zones in our study area. We compute $b$ and $M_{\max}$ using HA3 and the information from the catalog, which we divide in five sub-catalogs: one incomplete catalog for the prehistorical period before 1000, one incomplete catalog for the historical period between 1000 and 1799, one complete catalog for the early instrumental period between 1800 and 1899, and two complete catalogs for the instrumental periods between 1900 and 1999, and between 2000 and 2015. In this process we use the values of $M_c$ shown in Table \ref{tab:completeness}.

>>>>

The $a$-value is estimated based on the completeness year, the correlation distance, and the number of events per grid cell. We assume magnitude increments of $\Delta M = 0.1$, count events with magnitude $M_w > 3$, and smooth the number of events for each cell. This means each cell has a different $a$-value and thus the result is variable throughout our region of interest. On the other hand, we consider the $b$-value and $M_{\max}$ to be constant within each of the seismic zones in our study area. We compute $b$ and $M_{\max}$ using HA3 and the information from the catalog. \myrevision{ Regional maximum magnitude is estimated according to \citet{Kijko1989} method. Magnitude errors are distributed normally and $\beta$ and $\lambda$ are calculated simultaneously.  We divide the} catalog in five sub-catalogs: one incomplete catalog for the prehistorical period before 1000, one incomplete catalog for the historical period between 1000 and 1799, one complete catalog for the early instrumental period between 1800 and 1899, and two complete catalogs for the instrumental periods between 1900 and 1999, and between 2000 and 2015. In this process we use the values of $M_c$ shown in Table \ref{tab:completeness}.
